### 2012-09-28 doc/prelim/document/chapters/nonlinear_problem/nonlinear_problem.tex
finished draft of numerical experiments

As Newton methods are formulated independent of the inner linear
solver generating the Newton corrections, the actual performance of
the nonlinear iterations using MCSA is expected to be similar to that
of traditional Newton-Krylov methods. Furthermore, we expect to
achieve numerically identical answers with a Newton-MCSA method as
other Newton methods and we should indeed verify this. The parallel
performance of such a method will inherently be bound to the parallel
Monte Carlo implementation of the linear solver as the parallel
operations at the nonlinear iteration level are identical to those
that you would perform with a Newton-Krylov method. Matrix-free
formulations will have different parallel performance than these
methods, and therefore we should compare FANM perfomance to JFNK-based
schemes. More important than performance in the situation is the
reduced memory pressure that a FANM implementation provides, as
discussed in \S~\ref{subsec:fanm_storage}, because a FANM method will
not generate a subspace in the linear solver and compressed storage
for sparse matrices are utilized, we expect significant memory savings
over Newton-Krylov methods. We must measure the memory utilization of
both of these methods in order to quantify their differences and
provide additional analysis of the FANM method's merits, or lack
thereof.

>>>>

As Newton methods are formulated independent of the inner linear
solver generating the Newton corrections, the actual performance of
the nonlinear iterations using MCSA is expected to be similar to that
of traditional Newton-Krylov methods. Furthermore, we expect to
achieve numerically identical answers with a Newton-MCSA method as
other Newton methods and we should indeed verify this. The parallel
performance of such a method will inherently be bound to the parallel
Monte Carlo implementation of the linear solver as the parallel
operations at the nonlinear iteration level are identical to those
that you would perform with a Newton-Krylov method. Matrix-free
formulations will have different parallel performance than these
methods, and therefore we should compare FANM perfomance to JFNK-based
schemes. More important than performance in this situation is the
reduced memory pressure that a FANM implementation provides, as
discussed in \S~\ref{subsec:fanm_storage}, because a FANM method will
not generate a subspace in the linear solver and compressed storage
for sparse matrices are utilized, we expect significant memory savings
over Newton-Krylov methods. We must measure the memory utilization of
both of these methods in order to quantify their differences and
provide additional analysis of the FANM method's merits, or lack
thereof.

### 2012-09-28 doc/prelim/document/chapters/research_proposal/research_proposal.tex
finished draft of numerical experiments

\subsection{Parallel Performance and Numerical Accuracy Studies for FANM
  Method}
\label{subsec:fanm_studies}

>>>>

\subsection{Parallel Performance and Numerical Accuracy Studies for FANM
  Method}
\label{subsec:fanm_studies}
Aside from resiliency motivations, the primary driver behind the FANM
method is reduced memory pressure due to the lack of additional
storage beyond that of the linear system in the MCSA method. The
nonlinear benchmark problems we have chosen will let us measure this
memory usage and compare it to conventional Newton-Krylov
methods. Furthermore, by varying the strength of the nonlinearities in
those problems (effectively by increasing the amount of convective
transport in the system), the benchmarks will become more difficult to
solve and require even more iterations to converge. This will give us
a means by which to vary the complexity of the system which we can
then compare to memory usage. Additionally, with the finite element
assembly framework we can choose functional discretizations of varying
accuracy, allowing us to vary the degrees of freedom in the system and
therefore also vary the memory required.
